\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}
It is with great satisfaction and euphoria that we are submitting the Project Phase - II Report on \textbf{“Leveraging Blockchain for secure law enforcement and government records”}. We have completed it as a part of the curriculum of Visvesvaraya Technological University, Belagavi in partial fulfillment of the requirements for the VII semester of  Bachelor of Engineering in Computer Science and Engineering.
\par
\vspace{0.15in}
\noindent We are profoundly indebted to our guide, \textbf{Dr. Mustafa Basthikodi}, Professor \& Head, Department of Computer Science and Engineering for innumerable acts of timely advice, encouragement and we sincerely express our gratitude.
\par
\vspace{0.15in}
\noindent We also thank \textbf{Dr. Suhas A Bhyratae} and \textbf{Ms. Prapulla G}, Project Coordinators, Department of Computer Science and Engineering for their constant encouragement and support extended throughout.
\par
\vspace{0.15in}
\noindent We express our sincere gratitude to \textbf{Dr. Mustafa Basthikodi}, Professor \& Head, Department of Computer Science and Engineering for his invaluable support and guidance.
\par
\vspace{0.15in}
\noindent We sincerely thank  \textbf{Dr. S. S. Injaganeri}, Principal, Sahyadri College of Engineering and Management, who have always been a great source of inspiration.
\par
\vspace{0.15in}
\noindent Finally, yet importantly, we express our heartfelt thanks to our family and friends for their wishes and encouragement throughout the work.
\\
\\
\begin{flushright}
\textbf{Himanshu S Shetty (4SF22CS078)}\\
\textbf{M Imaad Iqbal (4SF22CS111)} \\
\textbf{Pratheek G Shetty (4SF22CS148)}\\
\textbf{Shifali Florine Lobo (4SF22CS192)}
\end{flushright}
\setstretch{1.4}