\chapter{Problem Formulation}

\section{Problem Statement}

Government legal records are critical assets that require secure, tamper-proof, and transparent handling. Traditional centralized record management systems are vulnerable to cyberattacks, unauthorized modifications, and data loss. These vulnerabilities undermine trust in judicial systems and delay legal proceedings. There is a pressing need for a secure, decentralized solution that ensures integrity, transparency, and traceability of legal documents.

\section{Problem Description}

The proposed project aims to address these issues by leveraging blockchain technology to build a secure and transparent framework for managing government legal records. Using Hyperledger Fabric, a permissioned blockchain platform, the system will ensure that access to legal data is strictly controlled and auditable. Smart contracts will automate document verification, timestamping, and access authorization, reducing human errors and procedural delays. The architecture includes a distributed ledger for tamper-proof recordkeeping, a client interface for user access, and secure APIs for system integration. The system also incorporates encryption services and identity management to safeguard sensitive data. This blockchain-based solution is expected to enhance efficiency, accountability, and public trust in legal and law enforcement institutions while addressing implementation challenges such as scalability, interoperability, and legal compliance.


\section{Objectives}

\begin{itemize}
    \item Develop a Hyperledger Fabric-based system for managing law enforcement records securely.
    \item Create a pipeline to hash documents and store files off-chain with on-chain hash verification.
    \item Implement smart contracts to automate legal processes such as evidence validation and warrant issuance.
    \item Apply role-based access control and maintain audit logs for all actions within the system.
    \item Assess scalability, legal compliance, and integration with existing government systems.
\end{itemize}
