\pagestyle{plain}
% Preamble (add this if not already included)
% In your main file where you want the references to appear:

\renewcommand{\bibname}{References}
\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{99}

\bibitem{liu}
Liu, S. and Zheng, Q. (2024). A study of a blockchain-based judicial evidence preservation scheme. \textit{Blockchain: Research and Applications}, 5, 100192.\\
\url{https://doi.org/10.1016/j.bcra.2024.100192}

\bibitem{nakamoto}
Nakamoto, S. (2008). Bitcoin: A Peer-to-Peer Electronic Cash System.\\
\url{https://bitcoin.org/bitcoin.pdf}

\bibitem{hyperledger}
Hyperledger Foundation. (n.d.). Hyperledger Blockchain Frameworks for Business and Government.\\
\url{https://www.hyperledger.org}

\bibitem{zheng}
Zheng, Z., Xie, S., Dai, H., Chen, X., and Wang, H. (2017). An overview of blockchain technology: Architecture, consensus, and future trends. \textit{Proceedings of the IEEE International Congress on Big Data}.\\
\url{https://doi.org/10.1109/BigDataCongress.2017.85}

\bibitem{tapscott}
Tapscott, D. and Tapscott, A. (2016). \textit{Blockchain Revolution: How the Technology Behind Bitcoin is Changing Money, Business, and the World}. Penguin Random House.
\\
\url{https://books.google.co.in/books/about/Blockchain_Revolution.html?id=NqBiCgAAQBAJ&redir_esc=y}

\bibitem{estonia}
Government of Estonia. (n.d.). Estonia’s Digital Government and Blockchain Implementation.\\
\url{https://e-estonia.com}

\bibitem{georgia}
Ministry of Justice, Georgia. (2017). Blockchain for Land Registry: A Case Study on Secure Government Records.\\
\url{https://gov.ge/blockchain-land-registry}

\bibitem{risius}
Risius, M. and Spohrer, K. (2017). A blockchain research framework: What we (don’t) know, where we go from here, and how we will get there. \textit{Business \& Information Systems Engineering}, 59(6), 385–409.\\
\url{https://link.springer.com/article/10.1007/s12599-017-0506-0}

\bibitem{atzori}
Atzori, M. (2017). Blockchain technology and decentralized governance: Is the state still necessary? \textit{Journal of Governance and Regulation}, 6(1), 45–62.\\
\url{http://dx.doi.org/10.22495/jgr_v6_i1_p5}

\bibitem{kshetri}
Kshetri, N. (2018). Blockchain’s roles in strengthening cybersecurity and protecting privacy. \textit{Telecommunications Policy}, 42(4), 335–344.\\
\url{https://doi.org/10.1016/j.telpol.2017.09.003}

\bibitem{nist}
Yaga, D., Mell, P., Roby, N., and Scarfone, K. (2018). Blockchain Technology Overview. \textit{National Institute of Standards and Technology (NIST)}.\\
\url{https://doi.org/10.6028/NIST.IR.8202}

\bibitem{swan}
Swan, M. (2015). \textit{Blockchain: Blueprint for a New Economy}. O’Reilly Media.\\
\url{https://books.google.co.in/books/about/Blockchain.html?id=ygzcrQEACAAJ&redir_esc=y}

\bibitem{sun}
Sun, J., Yan, J., and Zhang, K. Z. (2016). Blockchain-based sharing services: What blockchain technology can contribute to smart cities. \textit{Financial Innovation}, 2(26).\\
\url{http://dx.doi.org/10.1186/s40854-016-0040-y}

\bibitem{pilkington}
Pilkington, M. (2016). Blockchain technology: Principles and applications. In \textit{Research Handbook on Digital Transformations}. Edward Elgar Publishing.\\
\url{https://doi.org/10.4337/9781784717766}

\bibitem{europe}
European Commission. (2019). Blockchain for Digital Government: A European Perspective.\\
\url{https://ec.europa.eu/digital-strategy}

\bibitem{cong}
Cong, L. W. and He, Z. (2019). Blockchain disruption and smart contracts. \textit{The Review of Financial Studies}, 32(5), 1754–1797.\\
\url{https://doi.org/10.1093/rfs/hhz007}

\bibitem{zyskind}
Zyskind, G., Nathan, O., and Pentland, A. (2015). Decentralizing privacy: Using blockchain to protect personal data. \textit{IEEE Security and Privacy Workshops}, 180–184.\\
\url{https://doi.org/10.1109/SPW.2015.27}

\bibitem{bhaskar}
Bhaskar, N. D., and Chuen, D. L. K. (2017). \textit{Blockchain and Smart Contract for Digital Certification}. Springer.\\
\url{http://dx.doi.org/10.1007/978-3-031-22835-3}

\bibitem{saito}
Saito, T., and Yamada, T. (2016). What’s so different about blockchain? Decentralized trust and the future of digital transactions. \textit{Harvard Business Review}.\\
\url{https://hbr.org/2017/01/the-truth-about-blockchain}

\bibitem{yue}
Yue, X., Wang, H., Jin, D., Li, M., and Jiang, W. (2016). Healthcare data gateways: A blockchain-based secure data exchange architecture for healthcare information systems. \textit{Journal of Medical Systems}, 40(10), 218.\\
\url{https://doi.org/10.1016/j.jnca.2023.103633}

\bibitem{kassen}
Kassen, M. (2024). Blockchain and public service delivery: a lifetime cross-referenced model for e-government. \textit{Information Polity}.\\
\url{https://doi.org/10.1080/17517575.2024.2317175}

\bibitem{almamun}
Al Mamun, A., Azam, S., \& Gritti, C. (2022). Blockchain-Based Electronic Health Records Management: A Comprehensive Review and Future Research Direction. \textit{IEEE Access}.\\
\url{https://doi.org/10.1109/ACCESS.2022.3141079}

\bibitem{Sousa2023}
Sousa, M. J. (2023). Blockchain as a driver for transformations in the public sector. \textit{Journal of Innovation and Entrepreneurship}.\\
\url{https://doi.org/10.1080/25741292.2023.2267864}

\bibitem{dubai}
Khan, S., Shael, M., Majdalawieh, M., Nizamuddin, N., \& Nicho, M. (2022). Blockchain for Governments: The Case of the Dubai Government. \textit{Sustainability}, 14(11), 6576.\\
\url{https://doi.org/10.3390/su14116576}

\bibitem{tan2021}
Tan, E., Mahula, S., \& Crompvoets, J. (2022). Blockchain governance in the public sector: A conceptual framework for public management. \textit{Government Information Quarterly}, 39(1), 101625.\\
\url{https://doi.org/10.1016/j.giq.2021.101625}

\bibitem{kim2020}
Kim, T.-H., Kumar, G., Saha, R., Rai, M. K., Buchanan, W. J., \& Thomas, R. (2020). A Privacy Preserving Distributed Ledger Framework for Global Human Resource Record Management: The Blockchain Aspect. \textit{IEEE Access}.\\
\url{https://doi.org/10.1109/ACCESS.2020.2995481}

\bibitem{piao2021}
Piao, C., Hao, Y., Yan, J., \& Jiang, X. (2021). Privacy preserving in blockchain-based government data sharing: A Service-On-Chain (SOC) approach. \textit{Information Processing \& Management}, 58(5), 1026.\\
\url{https://doi.org/10.1016/j.ipm.2021.1026}

\bibitem{elisa2023}
Elisa, N., Yang, L., Chao, F., Naik, N., \& Boongoen, T. (2023). A Secure and Privacy-Preserving E-Government Framework Using Blockchain and Artificial Immunity. \textit{IEEE Access}.\\
\url{https://doi.org/10.1109/ACCESS.2023.3239814}

\bibitem{mahlaba2022}
Mahlaba, J., Mishra, A. K., Puthal, D., \& Sharma, P. K. (2022). Blockchain-Based Sensitive Document Storage to Mitigate Corruptions. \textit{IEEE Transactions on Engineering Management}.\\
\url{https://doi.org/10.1109/TEM.2022.3183867}

\bibitem{wang2024}
Wang, F., Gai, Y., \& Zhang, H. (2024). Blockchain user digital identity big data and information security process protection based on network trust. \textit{Journal of King Saud University - Computer and Information Sciences}.\\
\url{https://doi.org/10.1016/j.jksuci.2024.102031}




\end{thebibliography}
